Large Linear Multi-output Gaussian Process Learning for Time Series

### 2021-09-06 paper/paper.tex
final template gen

\documentclass[twoside]{article}
\usepackage{aistats2018}
% Camera ready: \usepackage[accepted]{aistats2018}
\newif\ifanonymized
\anonymizedtrue
% Camera ready: \anonymizedfalse

@@

\else
\subsubsection*{Acknowledgments}
(TODO) Thanks to Princeton, Cal, Prof. Joseph Gonzalez, Prof.Ion Stoica, Prof. Andrew Wilson, Prof. John Cunningham.
\fi

>>>>

\documentclass[twoside]{article}
\usepackage[arxiv]{aistats2018}
% Camera ready: \usepackage[accepted]{aistats2018}
\newif\ifanonymized
\anonymizedfalse
% Camera ready: \anonymizedfalse

@@

\else
\subsubsection*{Acknowledgments}
The authors would like to thank Princeton University and University of California, Berkeley, for providing the computational resources necessary to evaluate our method. Further, the authors owe thanks to Professors Joseph Gonzalez, Ion Stoica, Andrew Wilson, and John Cunningham for reviewing drafts of the paper and offering insightful advice about directions to explore.
\fi
